% Author: Alexander Patel 
% Description: Resume LaTeX source

\documentclass{res}
\topmargin=-0.5in
\addtolength{\textwidth}{0.8in}
\addtolength{\textheight}{8in}
\addtolength{\oddsidemargin}{-.5in}
\resumewidth=7.4in
\newsectionwidth{8pt}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Alexander H. Patel}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{(720) 320-1185}
\moveleft.5\hoffset\centerline{alexanderpatel@college.harvard.edu}

\begin{resume}

\section{EDUCATION}
    Bachelor of Arts, Philosophy and Mathematics, expected May 2018 (on leave 2015-2016) \\
    Harvard College, Cambridge, MA \\
    Minor: Computer Science \\
    GPA: 3.56/4.0 (Philosophy: 3.85/4.0 (4 courses), Mathematics: 3.85/4.0 (4 courses)) \\
    Relevant coursework: Operating Systems, Data Structures and Algorithms,
    Artificial Intelligence, Statistical Software, Discrete Mathematics, Linear
    Algebra, Real Analysis, Logic, Modal Logic. \\
    GRE M:165 V:164 \\
    SAT I: M:720 V:720 R:790 (SAT II: Math II:800 Physics:800)

\section{COMPUTER SKILLS}
    {\sl Languages:} Fluent: Python, C, R, SQL, Beginner: Javascript, Java \\
    {\sl Tools:} Unix Shell, Git, JIRA, Amazon AWS, NumPy/Pandas, Twisted
        networking framework, MySQL, Redis, Nginx, HTML/CSS, Latex. \\
    {\sl Skills:} asynchronous network programming, MySQL database
        administration, data ETL processes, Agile (Scrum) development,
        optimization and learning algorithms.
                
\section{WORK EXPERIENCE}
    {\sl Quantitative Software Engineer} \hfill {\sl September 2015 - September 2016} \\
    EverQuote (formerly Adharmonics), Cambridge, MA 

    \begin{itemize}  \itemsep -2.5pt

        \item Acted as technical lead for development of real-time bidding
            (RTB) bidder platform. Designed and implemented high-volume,
            low-latency ($<$100ms) networking server in Python.  Planned and
            organized project work for team of four engineers.  Coordinated
            technical platform integration with real-time auction exchanges.

        \item Implemented machine learning (esp. multi-armed bandit) algorithms
            for e-mail and banner display content optimization. 

         \item Earned 2nd place in company hackathon with real-time site
            arrivals geographic visualization.

    \end{itemize}
                 
    {\sl Software Engineering Intern} \hfill {\sl Summer 2015} \\
    Adharmonics, Cambridge, MA

    \begin{itemize} \itemsep -2.5pt

        \item Built third-party ad server for Google AdWords display
            advertising network. 

    \end{itemize} 

    {\sl Student Campaigns Organizer} \hfill {\sl May 2014 - May 2015} \\
    Free Software Foundation, Boston, MA

    \begin{itemize}   \itemsep -2.5pt 
        \item Coordinated developer action on Javascript licensing and Digital
            Rights Management campaigns. Authored technical issue posts topical
            to the free software community.

    \end{itemize} 

\section{TEACHING}
    {\sl Course Assistant} \hfill {\sl Spring 2016 - Present} \\
    Harvard Mathematics Department

    \begin{itemize} \itemsep -2.5pt
        \item Teaching staff member for Math E-23a: Linear Algebra and Real
            Analysis I (Fall 2016) and Math 156: Mathematical Foundations of
            Statistical Software (Spring 2016).

        \item Hosted weekly section and office hours; graded student R homework
            assignments and proof presentations.

    \end{itemize} 

    {\sl Teaching Fellow} \hfill {\sl 2015-2016} \\
    Harvard Computer Science Department

    \begin{itemize} \itemsep -2.5pt
        \item Teaching staff member for CS161: Operating Systems (Spring 2016)
            and CS61: Systems Programming (Fall 2015).

        \item Administered weekly section and office hours. Graded and assisted
            with student C programming assignments, design documents, and toy
            kernel implementations.

    \end{itemize} 

\section{EXTRA-CURRICULAR ACTIVITIES}      
    The Harvard Crimson, programmer for website Python back-end and news
    reporter on Harvard Business School beat\\
    % Harvard club lacrosse, midfield player \\
    Boston Museum of Science Computer Clubhouse, volunteer student mentor
 
\end{resume}
\end{document}
