% Author: Alexander Patel 
% Description: Resume LaTeX source

\documentclass{res}
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}
\topmargin=-0.5in
\addtolength{\textwidth}{0.8in}
\addtolength{\textheight}{8in}
\addtolength{\oddsidemargin}{-.4in}
\resumewidth=7.25in
\newsectionwidth{12pt}

% \makeatletter
% \def\section#1{\@@section{#1}\vskip .11cm}
% \makeatother

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Alexander H. Patel}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{(720) 320-1185}
\moveleft.5\hoffset\centerline{alexanderpatel@college.harvard.edu}
\moveleft.5\hoffset\centerline{\href{http://www.github.com/alexpatel}{www.github.com/alexpatel}}
\begin{resume}
\section{EDUCATION}
    \textbf{Harvard College}, Cambridge, MA \hfill {\sl Fall 2013 - Present}\\
    Bachelor of Arts, Philosophy and Mathematics, expected May 2018. Minor in Computer Science. \\
    GPA: 3.615/4.0 (Philosophy: 3.83/4.0 (7 courses), Mathematics: 3.88/4.0 (5 courses)). \\
    GRE M:165 V:164 W:4.0. \\
    Relevant coursework: linear algebra, real analysis, complex analysis,
    abstract algebra, combinatorics, probability theory, data structures and
    algorithms, systems programming, operating systems, artificial
    intelligence, logic, modal logic.
    % SAT I: M:720 V:720 R:790 (SAT II: Math II:800 Physics:800).

\section{TEACHING EXPERIENCE}
    {\sl Teaching Fellow} \\
    \textbf{Harvard University Computer Science Department}

    \begin{itemize} \itemsep -2.5pt
        \item Hosted weekly on-campus and virtual section and office hours.
            Graded and assisted with student C programming assignments and toy
            OS kernel implementations.
        \begin{itemize} \itemsep -2.5pt
            \item Computer Science 161: Operating Systems \hfill {\sl Spring 2017}
            \item Computer Science 161: Operating Systems \hfill {\sl Spring 2016}
            \item Computer Science 61: Systems Programming and Machine Organization \hfill {\sl Fall 2015}
        \end{itemize} 
    \end{itemize} 

    {\sl Course Assistant} \\
    \textbf{Harvard University Mathematics Department}
    \begin{itemize} \itemsep -2.5pt
        \item Administered weekly section and office hours. Graded student R homework
            assignments and proof presentations.
        \begin{itemize} \itemsep -2.5pt
            \item Math E-156: Mathematical Foundations of Statistical Software \hfill {\sl Spring 2017}
            \item Math E-23a: Linear Algebra and Real Analysis \hfill {\sl Fall 2016}
            \item Math 156: Mathematical Foundations of Statistical Software \hfill {\sl Spring 2016}
        \end{itemize} 
    \end{itemize} 

  
\section{WORK EXPERIENCE}
    {\sl Technology Consultant} \hfill {\sl September 2016 - Present} \\
    \textbf{Case Strategy, LLC}, Portsmouth, NH
    \begin{itemize}  \itemsep -2.5pt
        \item Served as technical advisor for strategy consulting platform
            powered by IBM Watson artificial intelligence service.
    \end{itemize}

    {\sl Quantitative Software Engineer} \hfill {\sl September 2015 - September 2016} \\
    \textbf{EverQuote (formerly Adharmonics)}, Cambridge, MA 
    \begin{itemize}  \itemsep -2.5pt
        \item Acted as technical lead for development of real-time bidding
            (RTB) bidder platform. Designed and implemented high-volume,
            low-latency ($<$100ms) networking server in Python. Organized
            project work for team of four engineers.  Coordinated technical
            platform integration with real-time auction exchanges.
        \item Implemented machine learning (esp. multi-armed bandit) algorithms
            for e-mail and banner display content optimization. 
         \item Earned 2nd place in company hackathon with real-time site
            arrivals geographic visualization.
    \end{itemize}

    {\sl Software Engineering Intern} \hfill {\sl Summer 2015} \\
    \textbf{Adharmonics}, Cambridge, MA
    \begin{itemize} \itemsep -2.5pt
        \item Built third-party ad server in Python for Google AdWords display
            advertising network. 
    \end{itemize} 

    % {\sl Student Campaigns Organizer} \hfill {\sl May 2014 - May 2015} \\
    % \textbf{Free Software Foundation}, Boston, MA
    % \begin{itemize}   \itemsep -2.5pt 
    %     \item Coordinated developer action on Javascript licensing and Digital
    %         Rights Management campaigns. Authored technical issue posts topical
    %         to the free software community.
    % \end{itemize} 

\section{EXTRA-CURRICULAR ACTIVITIES}      
    The Harvard Crimson, news reporter on Harvard Business School beat \hfill {\sl Fall 2013 - Spring 2015}\\
    The Harvard Crimson, programmer for website Python back-end \hfill {\sl Fall 2013 - Spring 2015}\\
    Boston Museum of Science Computer Clubhouse, volunteer student mentor \hfill {\sl Fall 2013 - Spring 2014}
    % Harvard Club Lacrosse, midfield player \hfill {\sl Fall 2013 - Fall 2014}

\section{COMPUTER SKILLS}
    {\sl Languages:} Python, R, C, SQL. Beginner: Ruby, Java. \\
    {\sl Tools:} Unix Shell, Git, NumPy/Pandas, Amazon AWS, vi, MySQL, Redis,
    Nginx, HTML/CSS, LaTeX.
      
\end{resume}
\end{document}
